Ktirio Urban Building: A Computational Framework for City Energy Simulations Enhanced by CI/CD Innovations on EuroHPC Systems

### 2024-10-25 article.hid2-ub-cicd.ppam24.tex
use cleveref

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}

@@

In \cref{fig:buildings}, we illustrate the different levels of details. \Cref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. \Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. Panel~\ref{fig:building-lod2} and~\ref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. In the figure~\ref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see panel~\ref{fig:city-strasbourg-lod0}, and LOD-1, see panel~\ref{fig:city-strasbourg-lod1}, representations.

>>>>

% Define custom color
\definecolor{CustomBlue}{rgb}{0.25, 0.41, 0.88} % RoyalBlue
% Set up hyperref with the custom citecolor
\hypersetup{
    pdftitle={\@title},
    pdfauthor={\@author},
    pdfsubject={\@subject},
    pdfkeywords={HPC, HPCOps, Urban building, City Energy Simulation},
    bookmarksnumbered,bookmarksopen,linktocpage,
    colorlinks=true,
    citecolor=CustomBlue,
    linkcolor=CustomBlue,
    urlcolor=blue
}
\usepackage{cleveref}

@@

In \cref{fig:buildings}, we illustrate the different levels of details. 
\Cref{fig:building-lod0} displays the LOD-0 of a building with its bounding box. 
\Cref{fig:building-lod1} displays the LOD-1 of a building using its footprint elevated to its height. 
\Cref{fig:building-lod2} and~\cref{fig:building-lod2-zoom} display the LOD-2 representation using BIM. 
In \Cref{fig:city-strasbourg}, we display an illustration of the center of the city of Strasbourg with LOD-0, see \cref{fig:city-strasbourg-lod0}, and LOD-1, see \cref{fig:city-strasbourg-lod1}, representations.
